---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# bbggplots

<!-- badges: start -->
[![R Build Status](https://github.com/erictleung/bbggplots/actions/workflows/R-CMD-check.yml/badge.svg)](https://github.com/erictleung/bbggplots/actions/workflows/R-CMD-check.yml)
[![License CC0](https://img.shields.io/cran/l/pixarfilms)](https://img.shields.io/cran/l/pixarfilms)
[![Project Type Toy Badge](https://img.shields.io/badge/project%20type-toy-blue)](https://project-types.github.io/#toy)
<!-- badges: end -->

> R data package to explore the cherry blossoms at the Brooklyn Botanic Garden

## Installation

You can install the development version of `bbggplots` from GitHub with:

```{r, eval = FALSE}
remotes::install_github("erictleung/bbggplots")
```

## Example

```{r}
library(bbggplots)
bbgdata
```

## Documentation

You can find information about the data sets and more
[here](https://erictleung.com/bbggplots/).
And , a list of vignettes showcasing some analyses you can do with this package
can be found [here](https://erictleung.com/bbggplots/articles/).


## Data

This data here within is not constrained to exploring just within R.

Here are direct links to each data set.

```
https://raw.githubusercontent.com/erictleung/bbggplots/main/data-raw/bbg_tree_bloom_2025.csv
```

## Feedback

If you have any feedback or suggestions on other data that can be added, please
file an issue [here](https://github.com/erictleung/bbggplots/issues).


## Code of Conduct

Please note that the {bbggplots} project is released with a
[Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

## Acknowledgments

- [Brooklyn Botanic Garden](https://bbg.org/)
