---
title: "Joining tables together"
author: Eric Leung
description: |
    This vignette demonstrates how to join tables together using the `dplyr` package. We will use the `bbgdata` and `treepositions` data frames from the `bbggplots` package to show how to merge information about the trees' bloom statuses with their spatial positions in the garden.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Joining tables together}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette demonstrates how to join tables together using the `dplyr` package. We will use the `bbgdata` and `treepositions` data frames from the `bbggplots` package to show how to merge information about the trees' bloom statuses with their spatial positions in the garden.

```{r setup}
library(bbggplots)
library(dplyr)
```

Here, we can pull data for 2025-04-14, which is the date of peak bloom for the cherry trees in that year. We will then join this data with the `treepositions` data frame to get the spatial coordinates of each tree.

```{r}
bbgdata |>
    filter(date == "2025-04-14") |>
    mutate(id = as.character(id)) |>
    left_join(treepositions, by = join_by(tree == tree, id == id))
```

Note, each of the tree positions here, which are encoded in the `top` and `left` columns, are in percentage coordinates corresponding to the background image of the garden map. Moreover, `top` here maps to the inverted y-axis (meaning positive values should be plotted with the negative complement to visualize normally) and `left` maps to the x-axis, which is a common convention for plotting images in R. This is something to keep in mind when plotting the data later on.

```{r}
sessionInfo()
```