---
title: "Plot cherry blossom bloom statuses"
author: Eric Leung
description: |
    This vignette demonstrates how to use the `bbggplots` package to visualize the bloom statuses of cherry trees in the Brooklyn Botanic Garden. We will use custom SVG icons to represent different bloom stages and plot them on a map of the garden.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot cherry blossom bloom statuses}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette demonstrates how to use the `bbggplots` package to visualize the bloom statuses of cherry trees in the Brooklyn Botanic Garden. We will use custom SVG icons to represent different bloom stages and plot them on a map of the garden.

This effectively is the code behind the `plot_map()` function, but here we will show how to do it step by step, and how to customize the plot further if desired.

```{r}
library(bbggplots)
library(dplyr)
library(ggplot2)
library(ggsvg)
library(ggpubr)
```

Each of the bloom stages (prebloom, first bloom, peak bloom, post bloom) has a corresponding SVG icon included in the package. We will read these SVG files into R and store them in a data frame for easy access.

```{r}
firstbloom_svg <-
    system.file("extdata", "cherry-firstbloom.svg", package="bbggplots") |>
    readLines(warn = FALSE) |>
    paste(collapse = "\n")
peakbloom_svg <-
    system.file("extdata", "cherry-peakbloom.svg", package="bbggplots") |>
    readLines(warn = FALSE) |>
    paste(collapse = "\n")
postbloom_svg <-
    system.file("extdata", "cherry-postbloom.svg", package="bbggplots") |>
    readLines(warn = FALSE) |>
    paste(collapse = "\n")
prebloom_svg <-
    system.file("extdata", "cherry-prebloom.svg", package="bbggplots") |>
    readLines(warn = FALSE) |>
    paste(collapse = "\n")
bg <-
    system.file("extdata", "cherrymap.png", package="bbggplots") |>
    png::readPNG()
```

Now, we will create a data frame that maps each bloom stage to its corresponding SVG icon. This will allow us to easily merge this information with our tree data later on.

```{r}
icons_df <- data.frame(
  bloom = c('Prebloom', 'First Bloom', 'Peak Bloom', 'Post Bloom'),
  svg  = c( prebloom_svg, firstbloom_svg, peakbloom_svg, postbloom_svg),
  stringsAsFactors = FALSE
)
```

And then finally, we can create the plot by filtering the data for a specific date, merging it with the tree positions and the icons, and then plotting it using `ggplot2` with the background image of the garden map.

```{r}
p_size <- 5
bg_dim <- dim(bg)
bbgdata |>
    filter(date == "2025-04-14") |>
    mutate(id = as.character(id)) |>
    left_join(treepositions, by = join_by(tree == tree, id == id)) |>
    mutate(
        x = (left / 100 * bg_dim[2]) + p_size,
        y = (-top / 100 * bg_dim[1]) - p_size
    ) |>
    merge(icons_df) |>
    ggplot() +
    background_image(bg) +
    geom_point_svg(
        aes(x = x, y = y, svg = I(svg)),
        size = p_size
    ) + 
    scale_x_continuous(
        expand = c(0, 0),
        limits = c(0, 550)
    ) +
    scale_y_continuous(
        expand = c(0, 0),
        limits = c(0, -498)
    ) +
    # Maintain 1:1 ratio and allow drawing outside limits
    coord_fixed(clip = "off") +
    theme_minimal()
```

```{r}
sessionInfo()
```